*Prochlorococcus marinus* responses to light and oxygen

### 2024-03-15 Code/Manuscript_O2.Rmd
Added to Data availabilty section

All data obtained from the Multicultivator were saved as comma separated
values files and are available at
<https://github.com/FundyPhytoPhys/prochlorococcus_o2/Data/RawData>.
Annotated code for data import, transformations and analyses are
available at
<https://github.com/FundyPhytoPhys/prochlorococcus_o2/Code>.

>>>>

All data obtained from the Multicultivator were saved as comma separated
values files and are available at
<https://github.com/FundyPhytoPhys/prochlorococcus_o2/Data/RawData/MultiCultiData1.zip>.
<https://github.com/FundyPhytoPhys/prochlorococcus_o2/Data/RawData/MultiCultiData2.zip>.
<https://github.com/FundyPhytoPhys/prochlorococcus_o2/Data/RawData/MultiCultiData3.zip>.
All data obtained from the Jaz spectrometer were saved as text files and are available at
<https://github.com/FundyPhytoPhys/prochlorococcus_o2/Data/RawData/JazEmData.zip>.
All data obtained from the Olis 14 UV/VIS Clarity Spectrophotometer were saved as ascii files and are available at
<https://github.com/FundyPhytoPhys/prochlorococcus_o2/Data/RawData/OlisData.zip>.
Meta Data for the Multicultivator runs were imported and saved as a .Rds and available at
<https://github.com/FundyPhytoPhys/prochlorococcus_o2/Data/RawData/CultureCatalog.Rds>.

Annotated code for data import, transformations and analyses are
available at
<https://github.com/FundyPhytoPhys/prochlorococcus_o2/Code>.
